A Framework for Equivalence of Cast Calculi and a new Cast Representation

### 2020-10-01 paper.tex
reorganization of the summary of contributions

To summarize, the primary contributions of this paper are:
\begin{itemize}
    \item Cast ADT, an abstract data type for cast representations
    \item a CEK abstract machine parameterized over Cast ADT
	\item a framework in Agda for proving the correctness of \LD\ or \LUD\ 
	cast representations when plugging into the CEK machine
	\item a formal proof that \LUD\ threesomes are correct
	\item a formal proof that \LUD\ coercions in normal form are correct
	\item hypercoercions, a new cast representation, which
	has a more compact memory representation in comparison to coercions in 
	normal form.
	\item a formal proof that both \LUD\ hypercoercions are correct
	\item a formal proof that both \LD\ hypercoercions are correct
\end{itemize}

>>>>

To summarize, the primary contributions of this paper are:
\begin{itemize}
\item Cast ADT, an abstract data type for cast representations, and a
  CEK abstract machine parameterized over the Cast ADT,
\item a framework in Agda for proving the correctness of cast
  representations,
\item hypercoercions, a new cast representation with a more compact
  memory representation compared to coercions in normal form, and
\item proofs of correctness in Agda for \LUD\ threesomes,
  \LUD\ coercions in normal form, \LUD\ hypercoercions, and
  \LD\ hypercoercions.
\end{itemize}
